Robust Control of a Fluxonium Qubit

### 2020-10-13 paper/main.tex
updated f1 figures

The optimizations for the $Y/2$ and $Z/2$ gates converge on similar solutions, a periodic
waveform with amplitude $\sim 0.2 \textrm{GHz}$, see Figure 1.
Both solutions extend their gate times
beyond their analytic counterpart, trading longer gate times for access
to higher amplitudes and therefore higher $T_{1}$ times. Both gates reduce
their single gate probability of longitudinal relaxation by a factor of $5$ over
their analytic counterparts, scaling similarly to their single gate error reduction
$3 \cdot 10^{-5} \rightarrow 7 \cdot 10^{-6}$, see Appendix.
The gate error reported in this text is the infidelity of the evolved state and the target state
averaged over multiple pseudo-randomly generated initial states.
Furthermore, they perform simlarly in
the concatenated gate application comparision, maintaining total gate errors under $10^{-2}$
over $10^{3}$ gate applications. Their single gate errors are sufficient for
quantum error correction, requisite for fault-tolerant quantum computing,
and their low gate errors for extend computations are critical for noisy, intermediate-scale
quantum (NISQ) applications.
The $T_{1}$ optimized $X/2$ gate achieves a single gate error...

@@

%% T1
\begin{table}[ht]
  \begin{tabular}{c | c | c | c | c | c | c}
         & Analytic & QOC & & Analytic & QOC & \\
    Gate & $P_{1}\ (10^{-5})$ & $P_{1}\ (10^{-5})$ & $P_{1\textrm{A}} / P_{1\textrm{Q}}$
    & GE $(10^{-5})$ & GE $(10^{-5})$ & GE$_{\textrm{A}}$ / GE$_{\textrm{Q}}$\\
    \hline
    Z/2 & 5.745  & 1.149 & 5.000 & 3.568  & 0.727 & 4.905\\
    Y/2 & 5.253  & 1.157 & 4.540 & 3.107  & 0.763 & 4.072\\
    X/2 & 16.251 & 4.488 & 3.621 & 10.542 & 3.563 & 3.449\\
  \end{tabular}
  \caption{Probability of longitudinal relaxation for each gate
    evaluated at the gate's duration.}
\end{table}

>>>>

The optimizations for the $Y/2$ and $Z/2$ gates converge on similar solutions, a periodic
waveform with amplitude $\sim 0.2 \textrm{GHz}$, see Figure 1.
Both solutions extend their gate times
beyond their analytic counterpart, trading longer gate times for access
to higher amplitudes and therefore higher $T_{1}$ times. Both gates reduce
their single gate probability of longitudinal relaxation by a factor of $5$ over
their analytic counterparts, scaling similarly to their single gate error reduction
$3 \cdot 10^{-5} \rightarrow 7 \cdot 10^{-6}$, see Appendix.
The gate error reported in this text is the infidelity of the evolved state and the target state
averaged over multiple pseudo-randomly generated initial states.
Furthermore, they perform simlarly in
the concatenated gate application comparision, maintaining total gate errors under $10^{-2}$
over $10^{3}$ gate applications. Their single gate errors are sufficient for
quantum error correction, requisite for fault-tolerant quantum computing,
and their low gate errors for extend computations are critical for noisy, intermediate-scale
quantum (NISQ) applications.

The $T_{1}$ optimized $X/2$ gate achieves a factor of 3.5 reduction in
its single gate probability of longitudinal relaxation over its analytic
counterpart, commensurate with its
reduction in single gate error $1 \cdot 10^{-4} \rightarrow 3.5 \cdot 10^{-5}$.
The analytic $X/2$ gate is composed of the analytic $Z/2$ and $Y/2$ gates $-Y/2 \cdot Z/2 \cdot Y/2$.
In principle the $T_{1}$ optimized $X/2$ gate should be able to perform at least as well
as the analogous composite of the $T_{1}$ optimized $Z/2$ and $Y/2$ gates, achieving a factor
of 5 reduction in its single gate probability and single gate errors.
For all of the gates optimized here, the longitudinal relaxation probability is an effective
metric in predicting performance in simulated relaxation and in decreasing the erro.

@@

%% T1
\begin{table}[ht]
  \begin{tabular}{c | c | c | c | c | c | c}
         & Analytic & QOC & & Analytic & QOC & \\
    Gate & $P_{1}\ (10^{-5})$ & $P_{1}\ (10^{-5})$ & $P_{1\textrm{A}} / P_{1\textrm{Q}}$
    & GE $(10^{-5})$ & GE $(10^{-5})$ & GE$_{\textrm{A}}$ / GE$_{\textrm{Q}}$\\
    \hline
    Z/2 & 5.745  & 1.149 & 5.000 & 1.776 & 0.371 & 4.787\\
    Y/2 & 5.253  & 1.157 & 4.540 & 1.539 & 0.370 & 4.159\\
    X/2 & 16.251 & 2.660 & 6.109 & 5.347 & 0.863 & 6.196\\
  \end{tabular}
  \caption{Probability of longitudinal relaxation for each gate
    evaluated at the gate's duration.}
\end{table}
